\vspace*{10pt}

\documentclass[a4paper, 12pt]{article}
\begin{document}

\subsection {{Exercise Form Correction}\hfill }
In-progress capstone application that corrects user exercise form. Flutter is used to develop an application for iOS and Android. The backend was created with Flask, and built into a docker container which is hosted on AWS. The backend uses Tensorflow's posenet model for keypoint recognition, then further uses a decision tree model to determine form correctness with SkLearn.
\subsection {{}\hfill }

\subsection {{KnowYourAlgo}\hfill }
Algorithm visualization game to teach players about algorithms. The website and game was built with JavaScript with framework React. The backend was created using Flask.
\subsection {{}\hfill }
\subsection {{Peer to Peer Image Sharing Network}\hfill }
p2p network built from scratch with JavaScript. Allows for multiple peers, each peer can search for images in the network and get them sent to them. 

\subsection {{}\hfill }

\subsection {{Game Store Management Tool}\hfill }
A game store management site for a hypothetical video game store manager. React.js was used to build a clean frontend interface. Express was used to develop a backend, which is hosted on Google Cloud. 
\subsection {{}\hfill }


\subsection {{Chatroom Application}\hfill }
This application utilizes the concepts of threads, semaphores and parallel processing in C++ to create a multi-user multi-transaction server and chat client. A user can run this C\#-based chat application on their device, communicating with other users over 9 different chat rooms and their desired username.
\subsection {{}\hfill }


\subsection {{Client-Server Image Network}\hfill }
Client server network architecture implementation. Server hosts multiple images, client asks server for image. Implemented specific packet objects in JavaScript.
\subsection {{}\hfill }

\subsection {{Temperate Ambient Light}\hfill }
Ambient light system prototype project. A light would change color based on temperature of the present environment and current season. Coded in C.
\subsection {{}\hfill }

\subsection {{Video Summary Application}\hfill }
 Designed and developed a framework for storing and analyzing videos. Built using React.js for the front facing application, with a Flask backend and ElasticSearch for user queries. 

\subsection {{}\hfill }
\subsection {{Object Detection of Military Relevant Objects}\hfill }
Developed an object segmentation model built on Detectron2 for specific objects. Objects were annotated via Labelbox and trained on. Different object detection methods(NMS, etc.) were applied to improve model performance, alongside feature augmentation.
\subsection {{}\hfill }


\subsection {{2D RPG in Unity}\hfill }
Designed and developed a 2D RPG game in Unity using C\# and the software development lifecycle. The application was planned out beforehand with design documents, then built in Unity over the term.
\subsection {{}\hfill }

\subsection {{Publisher Database Application}\hfill }
 Developed a Java GUI application for a hypothetical client, with functionality to interact with a SQL database to track various Publisher attributes.


\end{document}
